---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mytools.bruno2

<!-- badges: start -->
<!-- badges: end -->

The goal of {mytools.bruno2} is to provide basic function to quickly analyse the structure and basic statistical information of any dataset.

## Installation

You can install the development version of mytools.bruno2 from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("training-unhcr-n2/mytools.bruno2")
```

## Examples

Please use my_dataset: a dummy dataset to try the diferent functions of the package. 
This is a basic example which shows you how to solve a common problem:

```{r example}
library(mytools.bruno2)
# basic example code

## get_info_data provides basic information (dimension and column names)of the dataset

get_info_data(iris)

get_info_data(my_dataset)

## get_mean_ data provides the average of all numeric variables in the dataset
get_mean_data(iris)
get_mean_data(my_dataset)

```
